Paper 1

### 2022-07-13 scripts/Paper 1.Rmd
Add ET conversion to daily

input <- input %>% select(xlDateTime, Fe, Fg_Av, Fh, Fld, Flu, Fn, Fsu, Fsd, Precip, RH, Sws, Ta, Ts, VPD, Wd_SONIC_Av, Ws_SONIC_Av,ER_LT_all, GPP_LT,GPP_SOLO, NEE_LT, ET_EF ) # select met variables (add more as needed)
colnames(input) <- c('Timestamp', 'LE', 'G', 'H', 'LWin', 'LWout', 'NETRAD', 'SWout', 'SWin', 'Precip', 'RH', 'SWC', 'Ta', 'Ts', 'VPD', 'WD', 'WS', 'ER_LT', 'GPP_LT', 'GPP_SOLO', 'NEE_LT', 'ET')

input$Timestamp <- as.POSIXct(input$Timestamp, format= "%d/%m/%Y %H:%M") # change from character to POSIXct
input[,2:21] <- as.data.frame(sapply(input[,2:21], as.numeric)) # convert data frame from character to numeric

@@

```{r create daily mean dataframe, include=FALSE}
# add variables to this daily df as needed
input.daily <- input %>%
  drop_na(Timestamp) %>% # some NAs in the Timestamp for some reason. Need to look into
  ddply(c("Year", "jday", "month"), summarise,
        Precip = sum(Precip, na.rm = TRUE),
        SWin = sum(SWin),
        Ta.mean = mean(Ta, na.rm = TRUE),
        Ta.max = max(Ta, na.rm = TRUE),
        Ta.min = min(Ta, na.rm = TRUE),
        Ts.mean = mean(Ts, na.rm = TRUE),
        Ts.max = max(Ts, na.rm = TRUE),
        Ts.min = min(Ts, na.rm = TRUE),
        SWC = mean(SWC, na.rm = TRUE),
        RH = mean(RH, na.rm = TRUE),
        VPD = mean(VPD, na.rm = TRUE),
        ET = mean(ET, na.rm = TRUE),
        NEE_LT = mean(NEE_LT, na.rm = TRUE), #daily average umol m-2 s-1
        ER_LT = mean(ER_LT, na.rm = TRUE),
        GPP_LT = mean(GPP_LT, na.rm = TRUE)) %>%
  mutate(NEE_LT.gC = gofC.f(NEE_LT),  #converts to daily total NEE in g C CO2
         ER_LT.gC = gofC.f(ER_LT),
         GPP_LT.gC = gofC.f(GPP_LT))

>>>>

input <- input %>% select(xlDateTime, Fe, Fg_Av, Fh, Fld, Flu, Fn, Fsu, Fsd, Precip, RH, Sws, Ta, Ts, VPD, Wd_SONIC_Av, Ws_SONIC_Av,ER_LT_all, GPP_LT,GPP_SOLO, NEE_LT, ET) # select met variables (add more as needed)
colnames(input) <- c('Timestamp', 'LE', 'G', 'H', 'LWin', 'LWout', 'NETRAD', 'SWout', 'SWin', 'Precip', 'RH', 'SWC', 'Ta', 'Ts', 'VPD', 'WD', 'WS', 'ER_LT', 'GPP_LT', 'GPP_SOLO', 'NEE_LT', 'ET')

input$Timestamp <- as.POSIXct(input$Timestamp, format= "%d/%m/%Y %H:%M") # change from character to POSIXct
input[,2:22] <- as.data.frame(sapply(input[,2:22], as.numeric)) # convert data frame from character to numeric

@@

```{r create daily mean dataframe, include=FALSE}
# add variables to this daily df as needed
input.daily <- input %>%
  drop_na(Timestamp) %>% # some NAs in the Timestamp for some reason. Need to look into
  ddply(c("Year", "jday", "month"), summarise,
        Precip = sum(Precip, na.rm = TRUE),
        SWin = sum(SWin),
        Ta.mean = mean(Ta, na.rm = TRUE),
        Ta.max = max(Ta, na.rm = TRUE),
        Ta.min = min(Ta, na.rm = TRUE),
        Ts.mean = mean(Ts, na.rm = TRUE),
        Ts.max = max(Ts, na.rm = TRUE),
        Ts.min = min(Ts, na.rm = TRUE),
        SWC = mean(SWC, na.rm = TRUE),
        RH = mean(RH, na.rm = TRUE),
        VPD = mean(VPD, na.rm = TRUE),
        ET = mean(ET, na.rm = TRUE)* 86400,#daily total ET
        NEE_LT = mean(NEE_LT, na.rm = TRUE), #daily average umol m-2 s-1
        ER_LT = mean(ER_LT, na.rm = TRUE),
        GPP_LT = mean(GPP_LT, na.rm = TRUE)) %>%
  mutate(NEE_LT.gC = gofC.f(NEE_LT),  #converts to daily total NEE in g C CO2
         ER_LT.gC = gofC.f(ER_LT),
         GPP_LT.gC = gofC.f(GPP_LT))
